SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/details.tex
add ref #6

Another problem worthy of special attention is the case where parts of
the query has no connecting variable. Let us consider the
simple example of when two triple patterns do not share a variable:
\begin{verbatim}
?person foaf:name ?name .
?contribution dct:title ?title .
\end{verbatim}
When this is evaluated, it will cause what is known as a ``Cartesian
join'', in which the result will contain \emph{all} the solutions of
the first triple pattern joined with \emph{all} the solutions of the
second triple pattern. This will usually be a large result, and it is
also resource consuming to compute.

>>>>

Another problem worthy of special attention is the case where parts of
the query has no connecting variable. Let us consider the
simple example of when two triple patterns do not share a variable:
\begin{example}{BGP with Cartesian join}\label{ex:cartesian}
\begin{verbatim}
?person foaf:name ?name .
?paper  dct:title ?title .
\end{verbatim}
\end{example}
When this is evaluated, it will cause what is known as a ``Cartesian
join'', in which the result will contain \emph{all} the solutions of
the first triple pattern joined with \emph{all} the solutions of the
second triple pattern. This will usually be a large result, and it is
also resource consuming to compute.
